Path Analysis - Chapter 2

### 2016-01-12 sem_development.Rmd
Add rainfall data to UMCA plots data frame.

# Now I can join the data without duplicating variable names
umca_plots <- left_join(umca_plots, rs_temps, by = c("plotid", "sample_year"))
umca_plots <- left_join(umca_plots, summer_temps, by = c("plotid", "sample_year"))
umca_plots
```

>>>>

# Now I can join the data without duplicating variable names
umca_plots <- left_join(umca_plots, rs_temps, by = c("plotid", "sample_year"))
umca_plots <- left_join(umca_plots, summer_temps, by = c("plotid", "sample_year"))
names(umca_plots)

# Add rainfall data to UMCA plots data frame
names(rain_total)
names(rain_days)
umca_plots <- left_join(umca_plots, rain_total, by = c("plotid", "sample_year"))
umca_plots <- left_join(umca_plots, rain_days, by = c("plotid", "sample_year"))
summary(umca_plots)

filter(umca_plots, is.na(rain_tot_2d))
# NAs in rainfall data are from 2003
filter(umca_plots, sample_year == 2003)
# Only 7 plots w/UMCA sampled in 2003, so removing these records
umca_plots <- filter(umca_plots, sample_year != 2003)
```
